Patients with Left Hemispheric Intracerebral Hemorrhage are Less Likely to Receive Neurosurgical Intervention

### 2024-06-26 manuscripts/manuscript1_supplement.qmd
prior descriptions
Specified 4 priors, have to run prior predictive checks

```{r dags}

dag_aggressive

@@

## Prior Distribution Specification

We show prior predictive checks for 2(?) sets of priors.

### Default Priors

```{r default prior predictive check - neurosurgical intervention}
#| echo: false
#| fig-height: 12

avg_predictions(m_prior_default_neurosurgery, variables = "ich_laterality")

results_visual(m_prior_default_neurosurgery, "Prior Predictive Check - Neurosurgical Intervention")

@@

### Weakly Informative Priors

@@

results_visual(m_prior_informative_neurosurgery, "Prior Predictive Check - Neurosurgical Intervention")

>>>>

```{r dags}
#| echo: false

# dag_aggressive

@@

## Prior Distribution Definitions

```{r prior definitions}
#| echo: false
#| output: false

neutral_mean <- 0
neutral_sd <- 0.35
neutral_lower_OR <- exp(neutral_mean - (1.96 * neutral_sd))
neutral_upper_OR <- exp(neutral_mean + (1.96 * neutral_sd))

left_mean <- -0.22
left_sd <- 0.175
left_lower_OR <- exp(left_mean - (1.96 * left_sd))
left_upper_OR <- exp(left_mean + (1.96 * left_sd))

right_mean <- 0.18
right_sd <- 0.175
right_lower_OR <- exp(right_mean - (1.96 * right_sd))
right_upper_OR <- exp(right_mean + (1.96 * right_sd))

@@

In defining prior distributions, we generally followed suggestions from previous literature. [@zampieriUsingBayesianMethods2021; @kruschkeBayesianAnalysisReporting2021; @gelmanBayesianWorkflow2020] Specifically, we defined 4 sets of priors for each outcome:

**Neutral prior**: mean of **`r neutral_mean`** and standard deviation of **`r neutral_sd`**, centering around an OR of **`r exp(neutral_mean)`** and 95% of the the probability mass for the OR between **`r round(neutral_lower_OR, digits = 2)`** to **`r round(neutral_upper_OR, digits = 2)`**.

**Left hemisphere prior**: mean of **`r left_mean`** and standard deviation of **`r left_sd`**, centering around an OR of **`r round(exp(left_mean), digits = 2)`** and 95% of the the probability mass for the OR between **`r round(left_lower_OR, digits = 2)`** to **`r round(left_upper_OR, digits = 2)`**.

**Right hemisphere prior**: mean of **`r right_mean`** and standard deviation of **`r right_sd`**, centering around an OR of **`r round(exp(right_mean), digits =2)`** and 95% of the the probability mass for the OR between **`r round(right_lower_OR, digits = 2)`** to **`r round(right_upper_OR, digits =2)`**.

**Flat prior**: most mimics a frequentist analysis

```{r prior graphical summary}
#| echo: false
#| fig-height: 6

# Return dnorm(x) for 0 < x < 2, and NA for all other x
dnorm_limit <- function(x) {
  y <- dnorm(x)
  y[x < 0] <- NA
  return(y)
}

ggplot(data = tibble(x = -2:2), aes(x = x)) +
  geom_function(fun = dnorm, args = list(mean = -20, sd = 0.5), linewidth = 1) +
  # stat_function(fun = dnorm_limit, geom = "area", color = "orange", alpha = 0.2) +
  geom_vline(xintercept = -0.22, linetype = "dashed", color = "orange", linewidth = 1) +
  scale_x_continuous(breaks = seq(-2, 2, 0.5)) +
  theme_ich()

m_prior_informative_neurosurgery

### Neurosurgical Intervention

@@

ggplot(mutate(spread_draws(m_prior_informative_neurosurgery, b_ich_lateralityRight),
  ich_right_or = exp(b_ich_lateralityRight)
), aes(ich_right_or)) +
  geom_density(color = "#422f05", fill = "#E69F00") +
  scale_x_continuous(breaks = seq(-10, 10, 0.25)) +
  labs(
    title = "Odds Ratio - Right Hemisphere",
    y = NULL, fill = NULL
  ) +
  geom_vline(
    xintercept = 1, linetype = "dashed",
    color = "#999999", linewidth = 1
  ) +
  theme_ich() +
  theme(legend.position = "none")
